\section{Related Work}
\label{sec:related-work}

\paragraph{Inference-time prompt privacy.}
Prior sanitizers perturb prompts before submission via metric local DP over embeddings~\cite{yue2021santext,chen2022custext}, MLM sampling~\cite{dp-mlm}, context-aware bucket perturbation~\cite{wu2025capecontextawarepromptperturbation}, format-preserving numeric protection~\cite{chowdhury2025}, or token-level budget allocation~\cite{SYBW}; see~\cite{edemacu2025privacy} for a survey. All treat releases independently in single-turn settings. \sysname{} tracks dependencies across multi-turn interactions, noising only roots so that additional releases incur no additional cost.

\paragraph{DP under correlated data.}
Pufferfish~\cite{kifer2014pufferfish}, dependent DP~\cite{liu2016dependence}, Bayesian DP~\cite{zhao2019bayesian}, Wasserstein/Markov-Quilt mechanisms~\cite{song2017pufferfish}, R\'enyi composition~\cite{pierquin2024renyi}, and recent temporal/cross-sequence work~\cite{correlated2025csdp} all calibrate noise to account for statistical correlations \emph{between records}. Our correlations are functional, between \emph{releases} of one user's data, so we eliminate redundancy via post-processing rather than recalibrating noise.

\paragraph{Mechanisms.}
\sysname{} uses three metric DP~\cite{Chatzikokolakis2013BroadeningTS} mechanisms (discrete Exponential~\cite{mcsherry2007mechanism}, Bounded Laplace, Staircase~\cite{geng2015optimal}); our contribution is the sensitivity-weighted root allocation $\varepsilon_i \propto (|h_i| D_i)^{1/2}$, which is mechanism-agnostic (Sec.~\ref{sec:experiments-rq3}).

\paragraph{LLM agent privacy and security.}
Agentic systems face prompt injection~\cite{greshake2023indirect,zhan2024injecagent,debenedetti2024agentdojo,hou2025mcp} and multi-turn extraction attacks~\cite{zhang2025searchingprivacyrisks} on the MCP protocol~\cite{anthropic2024mcp}. Architectural defenses include AirGapAgent~\cite{bagdasarian2024airgapagent} (dual-LLM minimization), PAPILLON~\cite{siyan2025papillon} (local-remote proxy redaction), and CaMeL~\cite{debenedetti2025camel} (capability tracking). These enforce minimization empirically; \sysname{} provides formal guarantees that hold \emph{even when} unintended computations occur, since they are post-processing of noised roots. Broader LLM privacy risks --- training-data extraction~\cite{carlini2021extracting}, attribute inference~\cite{staab2024beyond}, contextual-norm violations~\cite{mireshghallah2024can,shao2024privacylens} --- motivate client-side sanitization in the first place.