\section{Conclusion}
\label{sec:conclusion}
We presented \sysname{}, a dependency-aware privacy mechanism for multi-turn agentic interactions: noise the roots once, compute everything else deterministically. Privacy then depends only on the initial root sanitization regardless of adversary function choices, query count, or turn order, while independent noising degrades with every additional release. The resulting double asymmetry --- additional turns simultaneously improve \sysname{}'s utility and degrade independent noising's privacy --- holds across 8 medical templates ($2.6$--$3.8\times$ lower wMAPE at $\varepsilon = 0.1$), across MAP reconstruction attacks ($\mathcal{M}$-All degrades from $16.5\%$ to $5.9\%$ as $q{:}1{\to}16$; \sysname{} invariant), and end-to-end through a 21{,}600-session LLM tool-call deployment (GPT-5.4 nano, $0\%$ compliance failures). The structural cause is simple: when one value flows through multiple service interactions, independent noising re-spends budget on each release while a dependency-aware mechanism spends it once. We believe this perspective should inform privacy design as agentic systems reach more sensitive domains.

\paragraph{Limitations and future work.}
We assume perfect NER for root identification, following prior sanitizers~\cite{chowdhury2025,wu2025capecontextawarepromptperturbation}; integrating noisy NER into the privacy analysis is open. Our evaluation covers structured numeric values in single-user sessions, one LLM backbone, one mechanism, and direct root queries; extending to free-form text, multi-user composition, additional backbones, and nonlinear derived-function attacks (which would tighten the $\mathcal{M}$-All vulnerability bound via Theorem~\ref{thm:privacy-leakage}) are natural next steps. Two further directions are promising: learning approximate target functions $\hat{g}$ from public population data when the exact formula is unknown, and composing \sysname{} with capability-based agent defenses~\cite{bagdasarian2024airgapagent,debenedetti2025camel} to combine formal DP with architectural minimization.